Soling at the 2000 Summer Olympics

### 2020-04-01 inst/soling.Rmd
consistentify

```{r loadlib}
library("hyper2")
data(soling)
soling_table_2000
ordertable_to_ranktable(soling_table_2000)
head(soling2000)
```

@@

now

```{r}
before <- maxp(soling2000)
soling2000 %<>% rr(soling2000_rr1)
soling2000 %<>% rr(soling2000_rr2)
soling2000 %<>% rr(soling2000_qf)
after <- maxp(soling2000)
par(pty="s")
plot(before,after,asp=1,pch=16,xlim=c(0,0.3),ylim=c(0,0.3))
abline(0,1)
```

>>>>

```{r loadlib}
library("hyper2")
data(soling)
H <- soling_table_2000
ordertable_to_ranktable(soling_table_2000)
head(soling2000)
```

@@

We can see the effect on the evaluate of incorporating the additional
observations into the Plackett-Luce likelihoods:

```{r}
H <- soling2000
before <- maxp(H)
H %<>% rr(soling2000_rr1)
H %<>% rr(soling2000_rr2)
H %<>% rr(soling2000_qf)
after <- maxp(H)
par(pty="s")
plot(before,after,asp=1,pch=16,xlim=c(0,0.3),ylim=c(0,0.3))
abline(0,1)
```

The diagram above shows a modest change.  We might ask whether the
additional observations are consistent with the original Placket-Luce
likelihood:

```{r}
(H2 <- H + (-1)*soling2000)
```
